### 2018-09-17 manuscript/methods.tex
demo of one line per sentence
will be much nicer for git

\section{Methods}
\subsection{Data}
Chromosome number data was obtained from the Chromosome Count Database (CCDB, \citet{rice_2015}) for all taxa from Solanaceae family. The records obtained were first cleaned using CCDBcurator R package \citep{zenilferguson_2017}, to those we aggregated independent data of chromosome numbers and breeding systems recorded and curated by Emma Goldberg and Boris Igi\'c  (citations for original sources can be found in the supplementary information). In total we obtained 14,000 records of chromosome number and breeding system than were curated semi automatically by CCDBcurator and by hand to score the chromosome number and the breeding system with the most reconciliation. Furthermore, for the majority of taxa ploidy was assigned according to information from original sources and Kew Royal Botanic Gardens C-value DNA (bennett citation here dataset and the original sources agreggated by Goldberg and Igi\'c. For taxa without ploidy information but with information about chromosome number we assigned ploidy based on multiplicity of chromosomes within the genus. For example, \textit{Solanum betaceum} did not include information about ploidy level but its number of chromosomes is 24, since $x=12$ is the base chromosome number of the \textit{Solanum} genus we assigned  \textit{Solanum betaceum} as diploid. Species with more than one ploidy level were assigned smallest most frequent ploidy level recorded. Domesticated taxa (i.e. \textit{Solanum lycopersicon}) were removed to avoid since they contained multiple ploidy levels due to domestication and not spontaneous polyploidy. The remainder of taxa was then matched to largest time-calibrated  phylogeny of Solanaceae and this process resulted in 595 taxa used in each of the diversification models.

>>>>

\section{Methods}

\subsection{Data}

Chromosome number data was obtained from the Chromosome Count Database (CCDB, \citet{rice_2015}) for all taxa from Solanaceae family.
The records obtained were first cleaned using CCDBcurator R package \citep{zenilferguson_2017}, to those we aggregated independent data of chromosome numbers and breeding systems recorded and curated by Emma Goldberg and Boris Igi\'c  (citations for original sources can be found in the supplementary information).
In total we obtained 14,000 records of chromosome number and breeding system than were curated semi automatically by CCDBcurator and by hand to score the chromosome number and the breeding system with the most reconciliation.
Furthermore, for the majority of taxa ploidy was assigned according to information from original sources and Kew Royal Botanic Gardens C-value DNA (bennett citation here dataset and the original sources agreggated by Goldberg and Igi\'c.
For taxa without ploidy information but with information about chromosome number we assigned ploidy based on multiplicity of chromosomes within the genus.
For example, \textit{Solanum betaceum} did not include information about ploidy level but its number of chromosomes is 24, since $x=12$ is the base chromosome number of the \textit{Solanum} genus we assigned  \textit{Solanum betaceum} as diploid. 
Species with more than one ploidy level were assigned smallest most frequent ploidy level recorded.
Domesticated taxa (\ie \textit{Solanum lycopersicon}) were removed to avoid since they contained multiple ploidy levels due to domestication and not spontaneous polyploidy.
The remainder of taxa was then matched to largest time-calibrated phylogeny of Solanaceae and this process resulted in 595 taxa used in each of the diversification models.
